Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2021-02-08 paper/main.tex
Added TL's changes

We used Modules for Experiments in Stellar Astrophysics
(\textsc{MESA}, version 12115) to establish a grid of stellar models. 
\textsc{MESA} is an open-source stellar evolution package which is undergoing active development. 
Descriptions of input physics and numerical methods
can be found in \citet{Paxton.Bildsten.ea2011, Paxton.Cantiello.ea2013, Paxton.Marchant.ea2015, Paxton.Schwab.ea2018, Paxton.Smolec.ea2019}.
We adopted the solar chemical mixture, $(Z/X)_{\odot}$ = 0.0181,
 provided by \citet{Asplund.Grevesse.ea2009}. 
The initial chemical composition was calculated by:
%
\begin{equation}
\log (Z_{\rm{init}}/X_{\rm{init}}) = \log (Z/X)_{\odot} + \rm{[M/H]_{init}}.  \\
\end{equation}
%
We used the \textsc{MESA} $\rho-T$ tables based on the 2005
update of OPAL EOS tables \citep{Rogers.Nayfonov2002} and OPAL opacity
supplemented by low-temperature opacity \citep{Ferguson.Alexander.ea2005}. The \textsc{MESA} ‘simple’ photosphere were used as the set of boundary conditions for modelling the atmosphere.
The mixing-length theory of convection was implemented, where 
$\alpha_{\rm MLT} = \ell_{\rm MLT}/H_p$ is the mixing-length parameter. 
We also applied the \textsc{MESA} predictive mixing scheme \citep{Paxton.Schwab.ea2018, Paxton.Smolec.ea2019} in the model computation.

@@

The PP model (without the Sun) favoured a mean mixing-length parameter of $\mu_\alpha \simeq 1.7$. Whereas, the PPS model yielded a higher value of $\mu_\alpha \simeq 1.9$ by $\sim 2$-$\sigma$. We found this was attributed to the addition of the Sun. The individual solar results for the PPS model yielded a value of $\mlt_\odot = 2.12\pm0.03$ which was considerably higher than the $\mlt$ obtained for the other stars in the sample (see Appendix \ref{sec:sun-res}). The solar value also exceeds typical solar calibrated values of $\sim 1.9$ for the same stellar evolution code \citep[see e.g.][]{Stancliffe.Fossati.ea2016}. However, these solar calibrations often consider additional observables such as helioseismic estimates of surface helium abundance and the convective zone depth, and additional physics which drive convective mixing.
% ------ TODO: ask Tanda for paragraph ------
% The reason for this is unclear, except that the difference we see between between solar $\mlt$ and the rest of the sample is not unique. Previous work on the LEGACY sample of \emph{Kepler} dwarfs found the best fitting $\mlt$ for their sample approximately 90 per cent of the solar calibrated value for one of their pipelines with similar model physics to this work \citep{SilvaAguirre.Lund.ea2017}.
Despite the difference in $\mu_\alpha$, the resulting spread in mixing-length for the PPS model $\sigma_\alpha \approx 0.13$ was double that of the PP model to cope with the high solar value. This implies that a large population spread in $\mlt$ could explain the difference we see. In other words, if we assume that the best-fitting $\mlt$ is normally distributed in our population, then the Sun lies within 2-$\sigma$ of the mean, among 95 per cent of all stars in the population.

>>>>

We used Modules for Experiments in Stellar Astrophysics
(\textsc{MESA}, version 12115) to establish a grid of stellar models. 
\textsc{MESA} is an open-source stellar evolution package which is undergoing active development. 
Descriptions of input physics and numerical methods
can be found in \citet{Paxton.Bildsten.ea2011, Paxton.Cantiello.ea2013, Paxton.Marchant.ea2015, Paxton.Schwab.ea2018, Paxton.Smolec.ea2019}.
We adopted the solar chemical mixture, $(Z/X)_{\odot}$ = 0.0181,
 provided by \citet{Asplund.Grevesse.ea2009}. 
The initial chemical composition was calculated by:
%
\begin{equation}
\log (Z_{\rm{init}}/X_{\rm{init}}) = \log (Z/X)_{\odot} + \rm{[M/H]_{init}}.  \\
\end{equation}
%
We used the \textsc{MESA} $\rho-T$ tables based on the 2005
update of OPAL EOS tables \citep{Rogers.Nayfonov2002} and OPAL opacity
supplemented by low-temperature opacity \citep{Ferguson.Alexander.ea2005}. The grey Eddington $T-\tau$ relation is used to determine boundary conditions for modelling the atmosphere. The mixing-length theory of convection was implemented, where 
$\alpha_{\rm MLT} = \ell_{\rm MLT}/H_p$ is the mixing-length parameter. 
We also applied the \textsc{MESA} predictive mixing scheme \citep{Paxton.Schwab.ea2018, Paxton.Smolec.ea2019} in the model computation.

@@

The PP model (without the Sun) favoured a mean mixing-length parameter of $\mu_\alpha \simeq 1.7$. Whereas, the PPS model yielded a higher value of $\mu_\alpha \simeq 1.9$ by $\sim 2$-$\sigma$. We found this was attributed to the addition of the Sun. The individual solar results for the PPS model yielded a value of $\mlt_\odot = 2.12\pm0.03$ which was considerably higher than the $\mlt$ obtained for the other stars in the sample (see Appendix \ref{sec:sun-res}). This result agrees with the 3D simulations \citep[e.g.][]{Trampedach.Stein.ea2014}, which predict lower $\mlt$ for stars with lower $\teff$ and higher $\log g$. However, the solar value also exceeds the reference solar calibrated values of $\approx 1.92$ for the same stellar evolution code \citep{Paxton.Bildsten.ea2011}. This is caused by the differences in adopted solar mixture, atmospheric boundary conditions and the treatment of convective mixing between this work and typical reference values.

% The solar value also exceeds typical solar calibrated values of $\sim 1.9$ for the same stellar evolution code \citep[see e.g.][]{Stancliffe.Fossati.ea2016}. However, these solar calibrations often consider additional observables such as helioseismic estimates of surface helium abundance and the convective zone depth, and additional physics which drive convective mixing.
% ------ TODO: ask Tanda for paragraph ------
% The reason for this is unclear, except that the difference we see between between solar $\mlt$ and the rest of the sample is not unique. Previous work on the LEGACY sample of \emph{Kepler} dwarfs found the best fitting $\mlt$ for their sample approximately 90 per cent of the solar calibrated value for one of their pipelines with similar model physics to this work \citep{SilvaAguirre.Lund.ea2017}.
Despite the difference in $\mu_\alpha$, the resulting spread in mixing-length for the PPS model $\sigma_\alpha \approx 0.13$ was double that of the PP model to cope with the high solar value. This implies that a large population spread in $\mlt$ could explain the difference we see. In other words, if we assume that the best-fitting $\mlt$ is normally distributed in our population, then the Sun lies within 2-$\sigma$ of the mean, among 95 per cent of all stars in the population.
